---
title: "Stats597 - Week 10"
author: "Udit Ennam"
date: "May 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question

Please write a Shiny app with the following features:

* a choice of which state to plot
* a choice of plotting either median household income (B19013_001), median gross rent (B25064_001), or the ratio of median gross rent to median household income

* a plot of the chosen variable in the chosen state.

You can make the plot using choroplethr, ggplot with geom_sf, or leaflet (if you want to try leaflet take a look at https://rstudio.github.io/leaflet/shiny.html). You can plot county or census tract data; if you use choroplethr I suggest sticking to county-level.

```{r}
library(shiny)
library(tidyverse)
library(tidycensus)
library(ggplot2)
# Disabling Scientific notation
options(scipen=999)

ui <- fluidPage(sidebarLayout(
  sidebarPanel(
    selectInput(
      inputId = "state",
      label = "Choose State",
      choices = c(
        'Alaska',
        'Alabama',
        'Arkansas',
        'Arizona',
        'California',
        'Colorado',
        'Connecticut',
        'District of Columbia',
        'Delaware',
        'Florida',
        'Georgia',
        'Hawaii',
        'Iowa',
        'Idaho',
        'Illinois',
        'Indiana',
        'Kansas',
        'Kentucky',
        'Louisiana',
        'Massachusetts',
        'Maryland',
        'Maine',
        'Michigan',
        'Minnesota',
        'Missouri',
        'Mississippi',
        'Montana',
        'North Carolina',
        'North Dakota',
        'Nebraska',
        'New Hampshire',
        'New Jersey',
        'New Mexico',
        'Nevada',
        'New York',
        'Ohio',
        'Oklahoma',
        'Oregon',
        'Pennsylvania',
        'Rhode Island',
        'South Carolina',
        'South Dakota',
        'Tennessee',
        'Texas',
        'Utah',
        'Virginia',
        'Vermont',
        'Washington',
        'Wisconsin',
        'West Virginia',
        'Wyoming'
      ),
      selected = "New Jersey"
    ),
    # Default value is 'Median Household Income'
    radioButtons(
      inputId = "plotType",
      label = "Plot",
      choices = c(
        "Median Household Income",
        "Median Gross Rent",
        "Ratio of Median Gross Rent to Median Household Income"
      ),
      selected = "Median Household Income"
    )
  ),
  
  mainPanel(plotOutput("main_plot"),
            tableOutput("results"))
),
titlePanel(" "))
server <- function(input, output, session) {
  output$main_plot <- renderPlot({
    state <- input$state
    plot_type <- input$plotType
    if (plot_type == "Median Household Income") {
      df_median_income <-
        get_acs(
          geography = "county",
          variables = c(median_income = "B19013_001"),
          state = state,
          geometry = TRUE
        )
      df_median_income %>%
        ggplot(aes(fill = estimate, color = estimate)) +
        geom_sf() + scale_fill_gradient(low = "#fff7f7", high = "#7f0000") + scale_color_gradient(low = "#fff7f7", high = "#7f0000") +
        ggtitle("Median Household Income") + guides(
          fill = guide_legend(title = "Median Household Income"),
          colour = guide_legend(title = "Median Household Income")
        ) + theme_light() + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + theme(plot.title = element_text(hjust = 0.5))
    }
    else if (plot_type == "Median Gross Rent") {
      df_median_rent <-
        get_acs(
          geography = "county",
          variables = c(median_rent = "B25064_001"),
          state = state,
          geometry = TRUE
        )
      df_median_rent %>%
        ggplot(aes(fill = estimate, color = estimate)) +
        geom_sf() + 
        scale_fill_gradient(low = "#f2fff6", high = "#004414") + scale_color_gradient(low = "#f2fff6", high = "#004414") + 
        ggtitle("Median Gross Rent") + guides(
          fill = guide_legend(title = "Median Gross Rent"),
          colour = guide_legend(title = "Median Gross Rent")
        ) + theme_light() + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + theme(plot.title = element_text(hjust = 0.5))
    }
    else{
      df_median_income <-
        get_acs(
          geography = "county",
          variables = c(median_income = "B19013_001"),
          state = state,
          geometry = TRUE
        )
      df_median_rent <-
        get_acs(
          geography = "county",
          variables = c(median_rent = "B25064_001"),
          state = state,
          geometry = TRUE
        )
      colnames(df_median_income)[4] <- "Income"
      colnames(df_median_rent)[4] <- "Rent"
      df <-
        inner_join(as.data.frame(df_median_income),
                   as.data.frame(df_median_rent),
                   by = "GEOID")
      df %>% mutate(Ratio = Rent / Income) -> df_ratio
      df_median_income$Ratio <- df_ratio$Ratio
      df_median_income %>% ggplot(aes(fill = Ratio, color = Ratio)) +
        geom_sf() + scale_fill_gradient(low = "#f0edf7", high = "#140044") + scale_color_gradient(low = "#f0edf7", high = "#140044") +
        ggtitle("Ratio of Median Gross Rent to Median Household Income")  + guides(
          fill = guide_legend(title = "Ratio of Median Gross Rent to Median Household Income"),
          colour = guide_legend(title = "Ratio of Median Gross Rent to Median Household Income")
        ) + theme_light() + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + theme(plot.title = element_text(hjust = 0.5))
    }
  })
}

shinyApp(ui = ui, server = server)
```
